Results_setup

### 2020-04-23 src/Result_Setup.Rmd
renaming stages

@@

@@

>>>>

#make DMC1 table
DMC1.mean.obs.L <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Early",],
                 .(category),
                 summarize,

                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.L$stage <- "Early"

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Late",],
                 .(category),
                 summarize, 
                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "Late"

@@

#high vs low group (L)
ttest.HighLow.L.pval <- t.test(DMC1.DF$total.count[( (DMC1.DF$stage == "Early") & ( ( DMC1.DF$strain == "MSM") | (DMC1.DF$strain == "PWD") ) )  ],
               DMC1.DF$total.count[( (DMC1.DF$stage == "Early") & ( ( DMC1.DF$strain == "WSB") | (DMC1.DF$strain == "G") | (DMC1.DF$strain == "KAZ") ) )]    )$p.value
# p-value =  0.002145

#high vs low group (Z)
ttest.HighLow.Z.pval <- t.test(DMC1.DF$total.count[( (DMC1.DF$stage == "Late") & ( ( DMC1.DF$strain == "MSM") | (DMC1.DF$strain == "PWD") ) )  ],
               DMC1.DF$total.count[( (DMC1.DF$stage == "Late") & ( ( DMC1.DF$strain == "WSB") | (DMC1.DF$strain == "G") | (DMC1.DF$strain == "KAZ") ) )]    )$p.value
# p-value = 0.6628

#dom vs musc (L) (2 subsp vs)
ttest.subsp.L <- t.test(DMC1.DF$total.count[(DMC1.DF$subsp == "Dom") & (DMC1.DF$stage == "Early")], DMC1.DF$total.count[(DMC1.DF$subsp == "Musc") & (DMC1.DF$stage == "Early")] )
# p-value = 0.003016

#dom vs musc (Z)
ttest.subsp.Z <- t.test(DMC1.DF$total.count[(DMC1.DF$subsp == "Dom") & (DMC1.DF$stage == "Late")], DMC1.DF$total.count[(DMC1.DF$subsp == "Musc") & (DMC1.DF$stage == "Late")] )
#p-value = 0.09588

#KAZ vs Dom (Z) (only 1 L cell)
ttest.KAZ.Dom.z <- t.test(DMC1.DF$total.count[(DMC1.DF$subsp == "Dom") & (DMC1.DF$stage == "Late")], 
      DMC1.DF$total.count[(DMC1.DF$strain == "KAZ") & (DMC1.DF$stage == "Late")] )

@@

-----

              ifelse(grepl("KAZ", DMC1.DF$strain), "Low",
            ifelse(grepl("PWD", DMC1.DF$strain), "High",
               ifelse(grepl("MSM", DMC1.DF$strain), "High","")))))
```

```{r MAIN.DMC1.plot, echo=FALSE, warning=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

#experimenting with ggboplot
everyday <- ggboxplot(DMC1.DF[DMC1.DF$stage != "P",], x = "strain", y = "total.count",
          color = "stage", palette = "jco",
          add = "jitter", short.panel.labs = FALSE)
  #library gpubr has functions to add in sig/test bars.

#change order

DMC1.DF$strain<- factor(DMC1.DF$strain, levels =c("LEW",
                      "WSB","G", "KAZ", "SKIVE","PWD","MSM"), order=T )

DMC1.boxplot <- ggplot(aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+
  geom_boxplot(alpha=.5) +geom_jitter()+ggtitle("DMC1 averages in juvenile mice")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

DMC1.boxplot
```

```{r plot.stage.ttest, echo=FALSE, warning=FALSE}

anno_df_stage = compare_means(total.count ~ stage, group.by = "rec_group", data = DMC1.DF[DMC1.DF$stage != "P",],method = "t.test") %>% mutate(y_pos = 300)
#

DMC1.bxlt_Z_to_L <- ggplot(DMC1.DF[DMC1.DF$stage != "P",], aes(x=stage, y=total.count)) + 
  geom_boxplot(position=position_dodge()) + 
  geom_point(aes(color=rec_group), position=position_jitterdodge()) +

  #facet_wrap(~stage, nrow=1) +

  ggsignif::geom_signif(
    data=anno_df_stage, 
    aes(xmin=group1, xmax=group2, annotations=p.adj, y_position=y_pos), 
    manual=TRUE
  )+ggtitle("Comparison of DMC1 means across high and low recombing groups")+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

#Musc.mouse.av <-  Mouse.Table_BivData_4MM %>%  filter(subsp == "Musc")

ttest.ZtoL <- t.test(DMC1.DF$total.count[(DMC1.DF$stage == "L")],
               DMC1.DF$total.count[(DMC1.DF$stage == "Z")]  )

DMC1.High.goup <-  DMC1.DF %>%  filter(rec_group == "High")

ttest.ZtoL.high <- t.test(DMC1.High.goup$total.count[(DMC1.High.goup$stage == "L")],
               DMC1.High.goup$total.count[(DMC1.High.goup$stage == "Z")]  )

DMC1.Low.goup <-  DMC1.DF %>%  filter(rec_group == "Low")

ttest.ZtoL.Low <- t.test(DMC1.Low.goup$total.count[(DMC1.Low.goup$stage == "L")],
               DMC1.Low.goup$total.count[(DMC1.Low.goup$stage == "Z")]  )
```
